---
title: "Exercise 6: Stroop analysis"
author: "Your name"
date: '`r Sys.Date()`'
output:
  html_document:
    code_folding: show
    number_sections: yes
    theme: cerulean
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load libraries
```{r warning=FALSE}
library(tidyverse)
library(ggplot2)
```

# Load data

Loading data
```{r warning=FALSE}
getwd() # make sure you're int the directory you think you are

#load your data in this chunk into a variable stroop_dat 

stroop_dat  <-
  list.files(path = "../data/", pattern = "*.csv",full.names = TRUE) %>% 
  map_df(~read.csv(.))
stroop_dat


```
# Part 2

## Write down below the shell command(s) you used to concatenate all the individual data into a single CSV file


# Part 3

## Compute correct RTs only

Whenever we look at RTs, we don't want to mix together RTs from correct and incorrect responses. Subset your data-frame to include only the correct responses. From now on, use this subsetted dataframe.
```{r}

```


## Some descriptive stats

What are the group RT means for congruent and incongruent trials?
```{r warning=FALSE}

```

What are the group means for congruent and incongruent broken down for the 2 `prop_incongruent` conditions?
```{r warning=FALSE}

```

Write code that lists all the subj_codes whose overall accuracies are less than one (i.e., less than 100%)
```{r warning=FALSE}


```

# Part 4

Use `pivot_wider()` to generate a data-frame containing separate the mean congruent and incongruent trials of each subject, and use mutate() to create an `incongruence_cost` column that is the difference between RTs on incongruent and congruent trials (incongruent-congruent). Sort it so that the subjects with the largest incongruent costs are listed first
```{r warning=FALSE}

```



## Bonus (1 pt)

A larger incongruence cost may come from people being really fasts on the congruent trials, really slow on incongruent trials, or both. Write some code to determine which of these three possibilities are true in these data.
```{r}

```


Now let's see if the incongruence advantage is different between the 25% and 50% incongruence conditions. 
Use pivot_wider() again, but this time to get separate incongruence advantage columns for the .25 and .50 prop_incongruent conditions. 
```{r}

```



# Part 5

## Graphing!

Generate a graph showing how the incongruent advantage varies by prop_incongruent (hint: use a line graph, not bars!)
```{r warning=FALSE}

```


Generate a graph showing how the incongruent advantage varies by orientation. What are you seeing?
```{r warning=FALSE}



```


Figure out an easy-to-interpret way of showing *both* the effect of orientation and the effect of prop_incongruent on the congruency advantage.
```{r warning=FALSE}



```


Show how the incongruency advantage varies with trial number. Is it getting larger? Smaller? Is the trend similar for the 25% nd 50% prop_incongruent condition?
```{r warning=FALSE}



```






